% Print the title with above letter information
%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}

\lettersection{Self Promotion}
During my first year at NYCU in the field of Computer Science, my passion for coding and machine learning algorithms flourished. I dedicated myself to honing my programming skills, delving into languages like C++ and Python, while also immersing myself in the intricacies of data structures and algorithms.

In my second year, I proudly represented my college at the ICPC Asia Taoyuan Regional Programming Contest, clinching a Bronze medal. Concurrently, I delved into research by collaborating with a laboratory on a project in partnership with NVIDIA. Termed "Meta RL for Multi-Objective Bayesian Optimization," this endeavor sought to leverage Reinforcement Learning and Transformer architecture to tackle the complexities of Multi-Objective Bayesian Optimization. Through this project, I gained invaluable experience in constructing ML algorithms using PyTorch and employing Transformer architectures.

Throughout my academic journey, I embarked on several projects within various courses. Noteworthy among them was the application of the Transformer RL algorithm to Quantitative Trading, the development of an AI agent proficient in playing GO, and the creation of a cellphone rating system using Django. These projects were instrumental in fortifying my self-learning abilities and enhancing my development skills.

Transitioning into my third year, I participated in the 2023 Meichu Hackathon—a collaborative competition that aligned me with Google for an Android accessibility project. Our goal was to design an app accessible to all users. As part of a cohesive team, we conceptualized and developed a voice-to-text transcript app capable of identifying different speakers—an innovation scarce in existing apps. I took charge of establishing server connections and deploying ML models, ensuring seamless functionality. Our efforts culminated in securing third place among many teams within the Google group during the Meichu Hackathon.

Beyond technical prowess, my leadership role as President of a student club and my involvement in the SITCON 2022 Agenda Committee have significantly contributed to my communication skills and collaborative aptitude.

In essence, I possess confidence in my abilities as a machine learning engineer and a team player. I earnestly request your consideration, believing that my blend of professionalism, creativity, and meticulous attention to detail could greatly benefit Line Taiwan.

Thank you for your time and consideration.

\end{cvletter}


%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter information
