%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Introduction to Artificial Intelligence Course Project} 
    {Apply Trajectory Transformer for Qutitative Trading} 
    {Hsinchu, Taiwan} 
    {May. 2023} 
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Developing Tool: Python, Pytorch}
        \item {Implementing some algorithms such as DQN, DDQN, Policy Gradient and Trajectory Transformer.}
        %\item {Trajectory Transformer is a method combine Transformer and RL techniques and have quite well performance.}
        \item {Project Link: https://github.com/KJLdefeated/Trajectory-Transformer-for-Quatitative-Trading}
      \end{cvitems}
    }
%---------------------------------------------------------
% \cventry
% {Side Project} 
% {TransformeRL-Implentation of Transformer RL} 
% {Hsinchu, Taiwan} 
% {Jul. 2023} 
% {
%   \begin{cvitems} % Description(s) of experience/contributions/knowledge
%     \item {Developing Tool: Python, Pytorch}
%     \item {GPT(Generative Pretrained Transformer) module have achieved well performance in Natural language processing. There are many works that combine Transformer and RL.}
%     \item {Implemented Decision Transformer, Trajectory Transformer, MultiGame Decision Transformer etc.(Add more works in the future.)}
%     \item {Project Link: https://github.com/KJLdefeated/TransformRL}
%   \end{cvitems}
% }

%---------------------------------------------------------
  \cventry
    {Theory of Computer Game Course Project}
    {Playing Chess Game using Monte Carlo Tree Search} 
    {Hsinchu, Taiwan} 
    {Nov. 2022} 
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Applied Monte Carlo Tree Search playing NoGo (A kind of chess game) with C++.}
        \item {Implemented optimization algorithms such as MCTS.}
        \item {Project Link: https://github.com/KJLdefeated/Playing-NoGO-using-Monte-Carlo-Tree-Search}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Database Course Project} 
    {Cellphone Rating System} 
    {Hsinchu, Taiwan} 
    {Dec. 2022} 
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Developing Tool: Python, Django, SQL, AWS, HTML, CSS, JavaScript}
        \item {A cellphone rating system to manage the cellphone data and offer users to rate their own cellphone.}
        \item {Project Link: https://github.com/KJLdefeated/Database-Final-project}
      \end{cvitems}
    }


%---------------------------------------------------------

\cventry
    {Meichu Hackathon Android Accessibility project} 
    {Multispeaker Transcription} 
    {Hsinchu, Taiwan} 
    {Oct. 2023}
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Developing Tool: Python, Pytorch, Kotlin, Java, Android Studio}
        \item {An Android app that identify the user who is speaking. Transcript the audio and display in the app.}
        \item {Deploy ML models to Android app.}
      \end{cvitems}
    }

\end{cventries}
